### 2021-08-05 paper/paper.tex

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}

@@

\todo{add Intel discussion}

\todo{alter slightly with MHD results}

\todo{Trixi runs need redone due to further improvements}

>>>>

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-Euler}
\end{figure}

@@

\todo{TODO: add Intel discussion} % TODO: Andrew

\todo{TODO: alter slightly with MHD results} % TODO: Andrew

\todo{TODO: \trixi runs need redone due to further improvements} % TODO: Andrew
